\cvsection{Experience}
\begin{cventries}
  \cventry
    {PhD Project: "The Effect of Microstructure and Impurities on Transport in Actinide Oxide Films"}
    {Postgraduate Research, Computational Chemistry (Prof Stephen C.Parker)}
    {Bath, England}
    {October 2016 - March 2019}
    {
      \begin{cvitems}
        \item{Computational chemistry project - \textbf{Applications} - Nuclear Waste Remediation, Energy Materials, Enviromental Chemistry.}
		    \item{During this project I ran large scale simulations on currently used and new materials in order to generate data that I used to make predictions about the behaviour and properties of these materials.}
		    \item{This has required the development of bespoke software designed for the specific needs of the project. Full details can be found on my github account (symmy596).}
      \end{cvitems}
    }

  \cventry
    {Postgraduate Teaching Assistant}
    {University of Bath Chemistry Department}    
    {Bath, England}
    {October 2016 - Present}
    {
      \begin{cvitems}
        \item{Throughout the duration of my PhD I have taught undergraduate chemists how to program, specifically focusing on high level programming in \textbf{Python} and low level programming in \textbf{fortran}.}
        \item{I developed a new masters level course focusing on using \textbf{Python} programming to better understand and make predictions about the behaviour of materials.}
        \item{Part of an ongoing project to develop a new masters course focusing on teaching students how to use \textbf{Python} in data analysis.}
      \end{cvitems}
    }

  \cventry   
    {Maths for Chemists Lecturer}
    {}
    {}
    {October 2016 - Present}
    {
      \begin{cvitems}
        \item
        {Delivery of workshops in fundamental mathematical concepts for chemists, ensuring that all chemistry first year students had a consistent mathematical background.} 
      \end{cvitems}
    }

  \cventry
    {Masters Research Project: "Cerium Oxide Nanozymes - A computational Study"}
    {Undergraduate Research, Computational Chemistry (Prof Stephen C.Parker)}
    {Bath, England}
    {October 2015 - June 2016}
    {
      \begin{cvitems}
        \item{Part of an international collaboration between the University of Bath, Univeristy of Kent and the Univeristy of Central Florida.} 
      \end{cvitems} 
    }
    
    \cventry
    {Summer Studentship}
    {Collaborative Computational Projects 5 (CCP5) Summer Studentship}
    {Bath, England}
    {June 2015 - October 2015}
    {
      \begin{cvitems}
        \item {Undergraduate studentship funded by CCP5.}
      \end{cvitems}
    }
\end{cventries}
