\cvsection{Career Summary}
\begin{cventries}
  \cventry
  {Fraym}
  {Lead Data Scientist}
  {Washington DC, USA}
  {Oct  2022 - ONGOING}
  {
    \begin{cvitems}
      \item {I manage a team of 3 research data scientists working on the methodology behind Fraym's products. We are specifically focussed on developing machine learning methods aimed at spatial interpolation, quantify errors accurately and develop forcasting methods.}
      \item {I work closely (in a hands on technical capacity) with our team of machine learning angineers and data engineers to help translate theoretical models into existing products as well as develop new pipelines and services.}
    \end{cvitems}
  }
  \cventry
    {Geollect}
    {Lead Data Scientist / Data Scientist}
    {Bristol, UK}
    {Dec 2021 - Oct 2022 / Oct 2020 - Dec 2021}
    {
      \begin{cvitems}
        \item {At Geollet I developed exceptional AWS skills and hugely expanded my existing software development skills. I also developed people management experience as well as experience in client engagement. It was an excellent role which allowed me to formalise the programming, machine learning and theoretical knowledge that I developed in my academic career.}
        \item {I managed a team of 3 data scientists and 2 data engineers. I was responsible for growing and managing this team, developing existing products, designing new research projects and implementing the companie's data strategy}
        \item {I was responsible for building and maintaining the companies ETL pipelines. I wrote Python packages and deployed them to AWS, utilising resources such as Terraform, Kinesis streams, S3, EC2, ECS, DynamoDB and RDS. Furthermore I also designed and built our database and API.}
        \item {I was the companie's main data science consultant and provided data science expertise to the UK special forces, the Royal Navy, the World Bank and several other customers in defence, manufacturing and financial services. This work involved web scraping, the construction of nosql databases, using machine learning to detect anomalies from acoustic data and designing algorithms to indentify specific instances of vessel behaviour from AIS data. I led all of these projects, in one instance this involved a team of Geollect data scientists and in another I led a team of data scientists from a partner organisation. I performed all liaisons with the clients, delivered updates and delivered the final products. Furthermore I was responsible for allocating resources and calculating the cost of services.}
        \item {I applied machine learning to AIS data (vessel location broadcasts) in order to both classify different types of marine activity (e.g., fishing, anchoring etc.) as well as identifying patterns. I have researched, built and deployed gaussian mixture models, clustering algorithms and neural networks.}
        \item {I led a project to combine AIS data with satellite imagery to build a database of AIS enriched vessel images. As part of this project I applied neural networks to satellite imagery to identify vessels within an image.}
        \item {I also engaged in more traditional data analysis. I have developed a 'digital port assessment' using AIS data, that for a given port provides statistics regarding vessel traffic into and out of that port. I employ my data visualisation skills to display this information statically in the form of graphs and tables, but also dynamically in the form of a dashboard.}
        \item {I conducted data led intelligence investigations in conjunction with the geospatial intelligence team. This involves identifying and analysing data to support the hypotheses of the investigations team. In a recent example of this I combined AIS data with weather data to understand cargo loss in the Pacific Ocean.}
        \item {I worked with the marketting team to produce technical articles or social media posts.}
        \item {I took part in client meetings as the technical lead and my role was to provide technical explanations of our products as well as understand the technical requirements of client requests.}
        \item {I represented the company at conferences where I gave talks about how Geollect is innovating in the tech space.}
      \end{cvitems}
    }
  \cventry
    {Universtiy of Bath}
    {Postdoctoral Research Associate}
    {Bath, UK}
    {January 2020 - October 2020}
    {
      \begin{cvitems}
        \item {I developed computational simulation and analysis techniques to aid in the prediction and discovery of new Li-ion battery materials.}
        \item {I Utilised machine learning models to predict the properties of theoretical battery materials. This work was in collaboration with other computational researchers at Bath university as well as researchers at the Universities of Oxford and Liverpool who were conducting the experimental side of the project.}
        \item {I am an advocate of research software engineering and open source software. During my academic career I developed and published two pieces of research software. I was also involved in the development of open source teaching material for computational chemistry and also for teaching software engineering practices to postgraduate students.}
        \item {I took part in the Faraday Institutes summer studentship scheme and secured £4000 of funding to hire an undergraduate student who worked on a short projected that I designed for the summer. I was responsible for writing the hiring advert, selecting candidates for interview and conducting the interviews. I then onboarded the successful candidate, taught them the programming skills required to complete the project and then oversaw the project as it progressed.}
        \item {During this time, I published four research papers, delivered presentations to both internal and external audiences and worked to and met deadlines set by my supervisors.}
      \end{cvitems}
    }
    \cventry
    {University of Bath}    
    {Postgraduate Teaching Assistant / Maths for Chemists Lecturer}
    {Bath, UK}
    {October 2016 - January 2020}
    {
      \begin{cvitems}
        \item{Throughout the duration of my PhD I taught undergraduate chemists how to program, specifically focusing on high level programming in Python and low level programming in fortran.}
        \item{I developed a new masters level course focusing on using Python programming to better understand and make predictions about the behaviour of materials.}
        \item{Part of a project to develop a new masters course focusing on teaching students how to use Python in data analysis.}
        \item
        {Delivery of workshops in fundamental mathematical concepts for chemists, ensuring that all chemistry first year students had a consistent mathematical background.} 
      \end{cvitems}
    }
\end{cventries}
