\cvsection{Skills}
\cvsubsection{Programming fluency}
	\begin{cvskills}
		\cvskill{Basic}{Ruby, SQL, HTML/CSS}
		\cvskill{Intermediate}{Python, Git, Fortran, Shell}
	\end{cvskills}
\cvsubsection{Software development}
	\begin{cvskills}
		\cvskill{surfinpy}{surfinpy is an open-source Python library to facilitate the analysis and visualisation of large scale ab initio calculation data. surfinpy has been published in the journal of open source software.}\vspace{-.3cm}\\
		\cvskill{polypy}{polypy is an open-source Python library to designed to analyse molecular dynamics simulation data. polypy is built to read large datasets associated with molecular dynamics trajectories and from these produce insghtful statistical information. polypy has been used in two pieces of published material science to data.}
	\end{cvskills}


\cvsubsection{Publications}
	\begin{itemize}
		\item{A. R. Symington, M. Molinari, J. S. Statham, J. Wu, S. C. Parker  \underline{The role of dopant segregation on the oxygen vacancy distribution and oxygen diffusion in CeO\textsubscript{2} grain boundaries}, \textbf{Journal of Physics: Energy}, 1, 4, (2019)}
		\item{A. R. Symington, M. Molinari, N. A. Brincat, N. R. Williams, S. C. Parker, \underline{Defect segregation facilitates oxygen transport at fluorite UO\textsubscript{2} grain boundaries}, \textbf{Phil. Trans. A}, 377, 2152, (2019)}
		\item{M. Molinari, A. R. Symington, D. C. Sayle, T. S. Sakthivel, S. Seal, S. C. Parker, \underline{Computer-Aided Design of Nanoceria Structures as Enzyme Mimetic Agents: The Role of Bodily Electrolytes on Maximising Their Activity}, \textbf{ACS Appl. Mater. Interfaces}, 2, 3 (2019)}
		\item{J. M. Flitcroft, A. R. Symington, M. Molinari, N. A. Brincat, N. R. Williams, S. C. Parker, \underline{Impact of Hydrogen on the Intermediate Oxygen Clusters and Diffusion in Fluorite Structured UO\textsubscript{2+x}}, \textbf{Inorganic Chemistry}, 58, 6, (2019)}
		\item{A. R. McCluskey, J. Grant, A. R. Symington, T. Snow, J. Doutch, B. J. Morgan, S. C. Parker, K. J Edler, \underline{An introduction to classical molecular dynamics simulation for experimental scattering users}, \textbf{J. Appl. Crys}, 52, 3, (2019)}
		\item{A. R. Symington, J. Tse, M. Molinari, A. Marmier, S. C. Parker, \underline{surfinpy: A Surface Phase Diagram Generator}, \textbf{Journal of Open Source Software}, 4, 1210, (2019)}
		\item{A. R. Symington, M. Molinari, S. Moxon, J. Flitcroft, D. C. Sayle, S. C. Parker, \underline{Strongly Bound Surface Water Affects the Shape Evolution of Cerium Oxide Nanoparticles}, in peer review, (2019)}
		\item{A. R. Symington, M.Molinari, S. C. Parker, \underline{Controlling Cerium Oxide Nanoparticle Morphology Using Carbonate Species.}, in peer review, (2019)}
	\end{itemize}

%\cvsubsection{Presentations}
%	\begin{itemize}
%	\item
%	\end{itemize}
